03 - Analyses coding

### 2022-06-13 scripts/r/03-analyses-coding.Rmd
♻️ - add code to upload refitted models to OSF

Now that the components have been downloaded, we can start refitting the models using the scripts in `scripts/r/04-refit/`.

>>>>

Now that the components have been downloaded, we can refit the models using the scripts in `scripts/r/04-refit/`.

Once all your models have been refitted, you can upload them to the OSF, in the Cache component, `models/refitted/` folder.

Here's some code that does that for you.

```{r upload-refitted}
cache <- osf_retrieve_node("wds2m")
refitted <- osf_ls_files(osf_ls_files(cache, type = "folder")) %>%
  filter(name == "refitted")
models <- list.files(
  "./data/analyses/models",
  full.names = TRUE
)

osf_upload(
  refitted,
  path = models,
  recurse = TRUE, conflicts = "skip", progress = TRUE, verbose = TRUE
)
```
